---
title: "Phase 1 Tables"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library(tidyverse)
library(tidycensus)
library(sf)
library(DT)
```

```{r}
v17 <- load_variables(2017, "acs5", cache = TRUE)

v17 %>% 
  datatable()
  
```

# Children age 5 and Under by Race and Ethnicity

# Children age 5 and Under by Household Income

Search for "POVERTY STATUS IN THE PAST 12 MONTHS BY SEX BY AGE"

# Number of Children age 5 and Under

B09001_001

# Children age 5 and Under by Household Type

Search for "OWN CHILDREN UNDER 18 YEARS BY FAMILY TYPE AND AGE"

# Children age 5 and Under by Household Size

# Children age 5 and Under by Urbanicity

- Chicago does age and race for counties and then converts counties to urban/suburban/rural

# Parents with children age 5 and Under by education attainment

# Children age 5 and Under by Nativity and Citizenship Status

# Parents with Children age 5 and Under by Nativity and Citizenship Status

# Children age 5 and Under by Primary Language